An efficient acyclic contact planner for multiped robots

### 2017-01-11 body/rbprm.tex
finished first revision of rbprm part

\subsection{Computing the guide path in $C_{reach}^0$}
$C_{Reach}^0$ can be sampled efficiently thanks to Eq.~\ref{eq:reachc}, and can thus be used with a standard motion planner.
Thus, the only significant change regarding a classical planner is to replace the collision checking with the \textit{rechability condition} when verifying
the drawn configurations and associated local paths.

However, to improve the sampling efficiency 
%~ while remaining probabilistically complete, 
we bias the sampling process to generate near-obstacle configurations, similarly to~\cite{Amato98choosinggood}.
%~ First, a configuration is set to a random point on the surface of one randomly chosen obstacle. The root location is then translated and rotated randomly until the \gls{reachc} is satisfied.
Our current implementation of these modifications is based on the Bi-RRT planner \citep{770022} provided by the HPP software.

Thanks to these modifications, the problem of planning a \gls{contact reachable} path is reduced to a geometric collision-checking problem, of low dimension (6 for HyQ, 8 for HRP-2 that has 2 joints in the torso).
%~ By doing this we can solve the problem with a sampling-based approach, in \gls{interactive} computation times.

>>>>

\subsection{Computing the guide path in $C_{reach}^0$}
$C_{Reach}^0$ can be sampled efficiently thanks to Eq.~\ref{eq:reachc}, and can thus be used with a standard motion planner.
Thus, the only significant change regarding a classical planner is to replace the collision checking with the \textit{reachability condition} when verifying
the drawn configurations and associated local paths.

\delst{However, to improve the sampling efficiency 
we bias the sampling process to generate near-obstacle configurations, similarly to cite{Amato98choosinggood}.}
Our current implementation of these modifications is based on the Bi-RRT planner \citep{770022} provided by the HPP software.

In this Section we have thus presented a guide path planner for the geometric root of a robot. This planner is implemented as low a dimensional sampling based 
algorithm. Given start and goal configurations, it outputs a continuous path for the root of the robot, such that for any configuration in the path there exists a joint
configuration that results in static equilibrium.
%~ Thanks to these modifications, the problem of planning a \gls{contact reachable} path is reduced to a geometric collision-checking problem, of low dimension (6 for HyQ, 8 for HRP-2 that has 2 joints in the torso).
%~ By doing this we can solve the problem with a sampling-based approach, in \gls{interactive} computation times.
